Scikit-learn: machine learning without learning the machinery

### 2014-06-30 article.tex
Iter paper

Goal: enable anybody to contribute, have a controlled process, grow.

Github, tests (link to travis)

Difficulty of getting credit, of rewarding properly the long tail of small
contributors, of finding funding. Problem of brain drain.

Difficulty of project scope (ideally: first cover all of statistical
learning classics \cite{elemstatlearn}) and default parameters

>>>>

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications --more than 200 contributors
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project thus is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on Github --\url{http://github.com}-- with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the travis platform
(\url{http://travis-ci.org}).

The open-source, community-driven model of scikit-learn has fantastically
payed off. However, we find that it does not fit in the standard
professional incentive structure, whether it be in academia or in the
industry. Indeed, getting due credit for grass-root, free, software that
"just works" is difficult. None of the grant proposals submitted to fund
development by core contributors have so far been accepted, and there is
no straightforward revenue model. Even more challenging is rewarding
properly the long tail of small contributors. Finally, active
contributors tend to be victim of the project's success, and be promoted
to leading positions which leave them little time.

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code comes with a significant maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
comes to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to integrate all classical methods that
are most useful for prediction tasks. We favor time-tested algorithm and
put great care in the choice of default parameters.
